\documentclass[10pt]{article}
\usepackage[tmargin=1.00cm, bmargin=1.00cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage{bibtopic}

\oddsidemargin -0in
\evensidemargin -0in
\textwidth=165mm
\textheight=228mm
\parindent 0pt

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

\newcommand{\mysec}[1]{\vspace{2em}\textsc{\large #1}\vspace{1mm}\hrule\vspace{2mm}}
\newcommand{\mysub}[3]{\textbf{#1} {#2} \hfill {\em #3}}
\newcommand{\myssub}[1]{\hspace*{2mm}\parbox{163mm}{#1}\vspace*{2mm}}

\begin{document}


\begin{center}
{\Large \textbf{\textsc{Baris Kasikci}}} \vspace{1mm} \\
{\em  Researcher} \\
Microsoft Research
\end{center}

\vspace{1em}

\hspace{0.8in}
\begin{tabular}{@{}p{2.5in}p{4in}}
21 Station Rd. & +44 (79) 448 488 47\\
Cambridge CB1 2FB & barisk@microsoft.com \\
United Kingdom & http://www.bariskasikci.org \\
\end{tabular}

%\vspace{1em}

\vspace{-5mm}

\mysec{Research Interests}

My research is centered around developing techniques, tools and environments that help build more reliable and secure software. I am interested in finding solutions that allow programmers to better reason about their code, and that efficiently detect bugs, classify them, and diagnose their root cause. I especially focus on bugs that manifest in production, because they are hard and time consuming. I am also interested in efficient runtime instrumentation, hardware and runtime support for enhancing system security, and program analysis under various memory models.

\vspace{-5mm}

\mysec{Education}

\mysub{Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL)}{}{Lausanne, Switzerland} \vspace*{1mm} \\
\myssub{\vspace{2mm}\textit{Ph.D. in Computer Science}\hfill Sep. 2010--Dec. 2015 \\
Thesis: Techniques for Detection, Root Cause Diagnosis, \\ \phantom{xxxxxx} and Classification of In-Production Concurrency Bugs \\
Advisor: Prof. George Candea} \vspace{1mm}

\mysub{Middle East Technical University (METU)}{}{Ankara, Turkey} \vspace*{1mm} \\
\myssub{\vspace{2mm}\textit{M.Sc. in Electrical and Electronics Engineering} \hfill Sep. 2006--Jun. 2009 \\
Thesis:  Variability Modeling in Software Product Lines \\
{\textit{Graduated with the top grade}} \\
Advisor: Prof. Semih Bilgen} \vspace*{1mm}

\myssub{\textit{B.Sc. in Electrical and Electronics Engineering} \hfill Sep. 2002--Jun. 2006 \\
Project: Embedded Target Estimation, Detection, and Tracking\\
{\textit{Graduated with High Honors}} \\
Advisor: Prof. Arzu Koc}

\vspace{-5mm}
\mysec{Awards and Honors}

\myssub{EuroSys Roger Needham Award for Best PhD. Thesis in Computer Systems in Europe \hfill 2016} \\
\myssub{Intel Corp. Software and Services Group, Grant \hfill 2014--2016} \\
\myssub{VMware Inc., Doctoral Fellowship \hfill 2014--2015} \\
\myssub{EPFL, Doctoral Fellowship \hfill 2010--2011} \\
\myssub{Scientific and Technological Research Council of Turkey, Master Scholarship \hfill 2006--2008} \\
\myssub{Middle East Technical University, Dean's High Honor List \hfill 2006} \\
\myssub{Middle East Technical University, \\ Award for Best Team Performance, Undergraduate Final Project  \hfill 2006} \\
\myssub{Turkish Customs Association, Scholarship \hfill 2002--2006} \\

\vspace{-7mm}
%\begin{spacing}{1.1}
\bibliographystyle{geo}
\begin{btSect}{header-standard,biblio-confs-journals}
\mysec{Peer-reviewed Publications}
\btPrintAll
\end{btSect}
%\end{spacing}

\mysec{Professional Service}

\mysub{Reviewer}{}{} \\
\myssub{\vspace{2mm}Transactions on Software Engineering \hfill 2015 \\
Transactions on Software Engineering and Methodology \hfill 2015} \\
\mysub{PC Member}{}{}\\
\myssub{\vspace{2mm}International Symposium on Software Testing and Analysis, Artifact Evaluation Committee \hfill 2014} \\
\mysub{Shadow PC Member}{}{} \\ 
\myssub{\vspace{2mm}EuroSys Conference on Computer Systems (EuroSys) \hfill 2013, 2015} \\
\mysub{External Reviewer}{}{} \\ 
\myssub{\vspace{2mm}Conference on Innovative Data Systems Research (CIDR)\hfill 2013\\
Intl. Conf. on Dependable Systems and Networks (DSN) \hfill 2011, 2013 \\
EuroSys Conference on Computer Systems (EuroSys) \hfill 2011, 2012 \\
Workshop on Hot Topics in Operating Systems (HotOS) \hfill 2011, 2013 \\
USENIX Annual Technical Conference (USENIX ATC) \hfill 2011 \\
Symposium on Cloud Computing (SOCC) \hfill 2012 \\
Symp. on Operating Systems Principles (SOSP) \hfill 2011. 2013 \\
Intl. SPIN Workshop on Model Checking of Software (SPIN) \hfill 2011} \\

\end{document}
